### 2020-05-22 doc/manuscript/MEE_manuscript.Rmd
update manuscript
added some draft figures

handling trees that died (current handling is inconsistent!)

@@

### Results

>>>>

handling trees that died ([issue 31](https://github.com/EcoClimLab/ForestGEO-climate-sensitivity/issues/31))

@@

### Results
![**Figure 1 | Growth sensitivity to DBH:** (a) $\Delta r$, (b) $\Delta AGB$ ](size_figure_sketch.png)

![**Figure 2 | Climate senstivity (SCBI example):** (a) Helcoski quilt plot, (b) Climwin panel a, (c) Climwin correlation (d) GLS output ](climate_figure_sketch.png)
